Towards Practical First-Order Model Counting

### 2024-04-24 doc/paper.tex
The abstract

\usepackage[backgroundcolor=lightgray]{todonotes}
\usepackage{listings}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{microtype}
\usepackage{mathtools}
\usepackage{forest}
\usepackage{siunitx}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage[inline]{enumitem}

@@

\DeclareMathOperator{\Doms}{Doms}
\DeclareMathOperator*{\argmin}{argmin} % TODO: soon to be removed

@@

\begin{abstract}
  TODO: at most 200 words
\end{abstract}

@@

We compare \Cranetwo{} (in both BFS and greedy modes) with \textsc{FastWFOMC}
and \textsc{ForcLift} on two problems previously considered by Dilkas and
Belle~\shortcite{DBLP:conf/kr/DilkasB23}: the function-counting problem from
\cref{example:functions} and the bijection-counting problem described below.
Note that comparing \Cranetwo{} and \textsc{FastWFOMC} on a larger set of
benchmarks is challenging because there is no automated way to translate a
formula in \FO{} or \Ctwo{} into \UFO{} (or even check if such an encoding is
possible). The experiments were run on an AMD~Ryzen~7~5800H processor with
\SI{16}{\gibi\byte} of memory and Arch Linux~6.8.2-arch2-1 operating system.
\textsc{FastWFOMC} was executed using Python~3.8.19 with Python-FLINT~0.5.0.

\paragraph{Benchmarks (probably for supplementary material).}
\begin{itemize}
  \item Bijections
        \begin{itemize}
          \item In \Ctwo:
                \begin{gather*}
                  \forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{. }P(x, y)\\
                  \forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{. }P(x, y)
                \end{gather*}
          \item In \UFO:
                \begin{gather*}
                  \forall x, y \in \Delta\text{. }R(x) \lor \neg P(x, y)\\
                  \forall x, y \in \Delta\text{. }S(x) \lor \neg P(y, x)\\
                  |P| = |\Delta|
                \end{gather*}
                with weights $w^{-}(R) = w^{-}(S) = -1$
          \item In \FO: see \cref{example:overall}
        \end{itemize}
\end{itemize}

\begin{figure}
  \centering
  \input{plot}
  \caption{The runtime data of WFOMC algorithms on domains of sizes
    $1, 2, \dots, 35$. Note that the $y$ axis is on a logarithmic
    scale.}\label{fig:plot}
\end{figure}
% TODO: rename permutations to bijections in the plot

\paragraph{Results.}
\begin{itemize}
  \item As shown in \cref{fig:plot}, the runtimes of all compilation-based
        algorithms remain practically constant in contrast to the rapidly
        increasing runtimes of \textsc{FastWFOMC}.
  \item Note that \Cranebfs{} is able to handle more instances than
        \textsc{ForcLift} (e.g., the bijection-counting problem in our
        experiments and other problems in my previous work).
  \item Although the search/compilation part is slower in \Cranetwo{} than in
        \textsc{ForcLift}, the difference is negligible.
  \item The runtimes of three out of four WFOMC algorithms appear constant
        because---for these counting problems and domain sizes---compilation
        time dominates inference time (recall that compilation time is
        independent of domain sizes). Indeed, the maximum inference time of both
        \Cranebfs{} and \Cranegreedy{} across these experiments is
        only \SI{4}{\milli\second}.
  \item The runtimes of \Cranetwo{} have lower variation than those of
        \textsc{ForcLift} because with \textsc{ForcLift} we compile the formula
        anew for each domain size whereas with \Cranetwo{} we compile it once
        and reuse the resulting C++ program for all domain sizes.
  \item As another point of comparison,---in at most
        \SI{41}{\second}---\Cranetwo{} scales up to domains of sizes \num{e4}
        and \num{3e5} in bijection- and function-counting problems, respectively
        (whereas \textsc{FastWFOMC} already takes longer with domains of
        sizes\dots)
\end{itemize}

\todo[inline]{maybe examine \textsc{ForcLift}'s scalability as well}

\todo[inline,caption={}]{
  Some reproducibility requirements to keep in mind:
  \begin{itemize}
    \item A motivation is given for why the experiments are conducted on the
          selected datasets.
    \item All novel datasets introduced in this paper are included in a data
          appendix.
    \item All datasets drawn from the existing literature (potentially including
          authors’ own previously published work) are accompanied by appropriate
          citations. (mention the counting quantifier paper and my KR paper)
    \item All source code implementing new methods have comments detailing the
          implementation, with references to the paper where each step comes
          from.
    \item This paper formally describes evaluation metrics used and explains the
          motivation for choosing these metrics.
    \item This paper states the number of algorithm runs used to compute each
          reported result.
  \end{itemize}
}

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item Maybe add some complete examples of C++ programs in the supplementary
          material.
    \item Later on:
          \begin{itemize}
            \item Eliminate (e.g., Emacs) warnings.
            \item must run it by all 3 other coauthors
            \item re-check submission instructions and formatting guidelines
            \item Full stop at the end of a single-sentence caption?
            \item cite the \textsc{Crane} paper (and other algorithms' papers)
                  where necessary
            \item Something to think about that could inspire some kind of
                  theorems: how can I assume that a domain is empty if there are
                  constants associated with it?
            \item consider turning small sections (e.g., Section 5) into
                  subsections of even paragraphs.
            \item Authors may submit a separate PDF with additional information
                  supporting their claims (such as proof details, additional
                  experimental results, further details on experimental design,
                  etc).
          \end{itemize}
  \end{itemize}
}

>>>>

\usepackage[backgroundcolor=lightgray]{todonotes} % TODO: remove
\usepackage{listings}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[capitalize,noabbrev]{cleveref}
\usepackage{microtype}
\usepackage{mathtools}
\usepackage{forest}
\usepackage{siunitx}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage[inline]{enumitem}

@@

\DeclareMathOperator{\Doms}{Doms}

@@

\begin{abstract}
  First-order model counting (FOMC) is the problem of counting the number of
  models of a sentence in first-order logic. Recently, a new algorithm for FOMC
  was proposed that, instead of simply providing the final count, generates
  definitions of (possibly recursive) functions, which can be evaluated with
  different arguments to compute the model count for any domain size. However,
  the algorithm did not include base cases in the recursive definitions. This
  work makes three contributions. Firstly, we demonstrate how to construct
  function definitions that include base cases by modifying the logical formulas
  used in the FOMC algorithm. Secondly, we extend the well-known circuit
  modification technique in knowledge compilation, known as smoothing, to work
  with the formulas corresponding to base cases and the recently proposed node
  types, such as domain recursion and constraint removal. Thirdly, we introduce
  a compilation algorithm that transforms the function definitions into C++
  code, equipped with arbitrary-precision arithmetic. These additions allow the
  new FOMC algorithm to scale to domain sizes over \num{9000} times larger than
  the current state of the art, as demonstrated through experimental results.
\end{abstract}

@@

We compare \Cranetwo{} (in both BFS and greedy modes) with \textsc{FastWFOMC}
and \textsc{ForcLift} on two problems previously considered by Dilkas and
Belle~\shortcite{DBLP:conf/kr/DilkasB23}: the function-counting problem from
\cref{example:functions} and the bijection-counting problem described below.
Note that comparing \Cranetwo{} and \textsc{FastWFOMC} on a larger set of
benchmarks is challenging because there is no automated way to translate a
formula in \FO{} or \Ctwo{} into \UFO{} (or even check if such an encoding is
possible).

The \FO{} formula for bijections is described in \cref{example:overall}. The
equivalent formula in \Ctwo{} is
\begin{gather*}
  \forall x \in \Delta\text{. }\exists^{=1} y \in \Delta\text{. }P(x, y)\\
  \forall y \in \Delta\text{. }\exists^{=1} x \in \Delta\text{. }P(x, y).
\end{gather*}
Similarly, in \UFO{} the same formula can be written as
\begin{gather*}
  \forall x, y \in \Delta\text{. }R(x) \lor \neg P(x, y)\\
  \forall x, y \in \Delta\text{. }S(x) \lor \neg P(y, x)\\
  |P| = |\Delta|,
\end{gather*}
where $w^{-}(R) = w^{-}(S) = -1$.

We run each of the four algorithms once on each combination of formula and
domain size, the latter ranging from one up to and including 35. The experiments
were run on an AMD~Ryzen~7~5800H processor with \SI{16}{\gibi\byte} of memory
and Arch Linux~6.8.2-arch2-1 operating system. \textsc{FastWFOMC} was executed
using Python~3.8.19 with Python-FLINT~0.5.0.

\begin{figure}
  \centering
  \input{plot}
  \caption{The runtime of WFOMC algorithms. Note that the $y$ axis is on a
    logarithmic scale.}\label{fig:plot}
\end{figure}

\Cref{fig:plot} shows total runtime values as a measure of the overall
performance of each algorithm. For the three knowledge compilation algorithms,
we also separately track compilation and inference times and comment on them
where relevant. Note that \Cranebfs{} is able to handle more instances than
either \textsc{ForcLift} or \Cranegreedy{}, i.e., the bijection-counting problem
in our experiments as well as similar formulas examined
previously~\cite{DBLP:conf/kr/DilkasB23}.

As shown in the figure, the runtimes of all compilation-based algorithms remain
practically constant in contrast to the rapidly increasing runtimes of
\textsc{FastWFOMC}. Although the search/compilation part is slower in
\Cranetwo{} than in \textsc{ForcLift}, the difference is negligible. The
runtimes of the knowledge compilation algorithms appear constant because---for
these counting problems and domain sizes---compilation time dominates inference
time (recall that compilation time is independent of domain sizes). Indeed, the
maximum inference time of both \Cranebfs{} and \Cranegreedy{} across these
experiments is only \SI{4}{\milli\second}. The runtimes of \Cranetwo{} have
lower variation than those of \textsc{ForcLift} because with \textsc{ForcLift}
we compile the formula anew for each domain size whereas with \Cranetwo{} we
compile it once and reuse the resulting C++ program for all domain sizes.

As another point of comparison, we examine the maximum domain size that the
algorithms can handle in at most \SI{45}{\second} of total runtime. For
bijection-counting, \textsc{FastWFOMC} scales up to domains of size 28, whereas
\Cranebfs{} can handle domains of size \num{e4}. In the case of
function-counting, \textsc{FastWFOMC} can handle domains of size 32, whereas
\Cranebfs{} can handle \num{3e5}. On function-counting, \textsc{ForcLift} can
handle domains sizes up to about 100, but then the finite-precision arithmetic
declares higher model as infinite.

\todo[inline,caption={}]{
  \begin{itemize}
    \item Add info about \textsc{ForcLift} (taking care of infinities)
    \item Turn the above paragraph into a table.
    \item Mention two types of experiments earlier in the section.
  \end{itemize}
}

@@

\todo[inline,caption={}]{
  \begin{itemize}
    \item Later on:
          \begin{itemize}
            \item Eliminate (e.g., Emacs) warnings.
            \item must run it by all 3 other coauthors
            \item re-check submission instructions and formatting guidelines
            \item Full stop at the end of a single-sentence caption?
            \item cite the \textsc{Crane} paper (and other algorithms' papers)
                  where necessary
            \item Something to think about that could inspire some kind of
                  theorems: how can I assume that a domain is empty if there are
                  constants associated with it?
            \item consider turning small sections (e.g., Section 5) into
                  subsections of even paragraphs.
            \item Authors may submit a separate PDF with additional information
                  supporting their claims (such as proof details, additional
                  experimental results, further details on experimental design,
                  etc).
          \end{itemize}
  \end{itemize}
}

### 2024-04-24 doc/plot.tex
The abstract

% Created by tikzDevice version 0.12.6 on 2024-04-12 11:27:55
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (240.29,135.16);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 52.07) --
	( 37.66, 52.04) --
	( 40.67, 52.04) --
	( 43.67, 52.04) --
	( 46.68, 52.04) --
	( 49.68, 52.05) --
	( 52.69, 52.04) --
	( 55.70, 52.05) --
	( 58.70, 52.04) --
	( 61.71, 52.04) --
	( 64.71, 52.04) --
	( 67.72, 52.04) --
	( 70.73, 52.04) --
	( 73.73, 52.04) --
	( 76.74, 52.05) --
	( 79.74, 52.05) --
	( 82.75, 52.04) --
	( 85.75, 52.04) --
	( 88.76, 52.09) --
	( 91.77, 52.05) --
	( 94.77, 52.05) --
	( 97.78, 52.05) --
	(100.78, 52.05) --
	(103.79, 52.04) --
	(106.80, 52.04) --
	(109.80, 52.04) --
	(112.81, 52.04) --
	(115.81, 52.04) --
	(118.82, 52.04) --
	(121.82, 52.05) --
	(124.83, 52.05) --
	(127.84, 52.05) --
	(130.84, 52.04) --
	(133.85, 52.05) --
	(136.85, 52.04);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 54.53) --
	( 37.66, 54.50) --
	( 40.67, 54.50) --
	( 43.67, 54.49) --
	( 46.68, 54.49) --
	( 49.68, 54.49) --
	( 52.69, 54.49) --
	( 55.70, 54.50) --
	( 58.70, 54.50) --
	( 61.71, 54.49) --
	( 64.71, 54.49) --
	( 67.72, 54.49) --
	( 70.73, 54.49) --
	( 73.73, 54.49) --
	( 76.74, 54.50) --
	( 79.74, 54.50) --
	( 82.75, 54.50) --
	( 85.75, 54.50) --
	( 88.76, 54.49) --
	( 91.77, 54.50) --
	( 94.77, 54.50) --
	( 97.78, 54.49) --
	(100.78, 54.50) --
	(103.79, 54.50) --
	(106.80, 54.50) --
	(109.80, 54.50) --
	(112.81, 54.49) --
	(115.81, 54.50) --
	(118.82, 54.50) --
	(121.82, 54.50) --
	(124.83, 54.50) --
	(127.84, 54.50) --
	(130.84, 54.50) --
	(133.85, 54.50) --
	(136.85, 54.50);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 49.39) --
	( 37.66, 49.33) --
	( 40.67, 49.33) --
	( 43.67, 49.33) --
	( 46.68, 49.33) --
	( 49.68, 49.33) --
	( 52.69, 49.33) --
	( 55.70, 49.35) --
	( 58.70, 49.35) --
	( 61.71, 49.33) --
	( 64.71, 49.33) --
	( 67.72, 49.33) --
	( 70.73, 49.33) --
	( 73.73, 49.33) --
	( 76.74, 49.33) --
	( 79.74, 49.35) --
	( 82.75, 49.35) --
	( 85.75, 49.35) --
	( 88.76, 49.33) --
	( 91.77, 49.33) --
	( 94.77, 49.33) --
	( 97.78, 49.33) --
	(100.78, 49.33) --
	(103.79, 49.33) --
	(106.80, 49.35) --
	(109.80, 49.35) --
	(112.81, 49.33) --
	(115.81, 49.33) --
	(118.82, 49.33) --
	(121.82, 49.33) --
	(124.83, 49.33) --
	(127.84, 49.33) --
	(130.84, 49.35) --
	(133.85, 49.35) --
	(136.85, 49.33);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 29.90) --
	( 37.66, 30.63) --
	( 40.67, 30.63) --
	( 43.67, 29.90) --
	( 46.68, 30.63) --
	( 49.68, 31.33) --
	( 52.69, 32.63) --
	( 55.70, 33.82) --
	( 58.70, 35.45) --
	( 61.71, 38.26) --
	( 64.71, 40.62) --
	( 67.72, 42.34) --
	( 70.73, 46.05) --
	( 73.73, 49.23) --
	( 76.74, 52.36) --
	( 79.74, 64.35) --
	( 82.75, 58.30) --
	( 85.75, 68.19) --
	( 88.76, 70.67) --
	( 91.77, 72.59) --
	( 94.77, 78.45) --
	( 97.78, 78.57) --
	(100.78, 83.81) --
	(103.79, 86.56) --
	(106.80, 85.94) --
	(109.80, 92.57) --
	(112.81, 95.46) --
	(115.81, 98.41) --
	(118.82,102.64) --
	(121.82,102.38) --
	(124.83,106.28) --
	(127.84,110.72) --
	(130.84,112.06) --
	(133.85,116.16) --
	(136.85,119.03);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 30.63) --
	( 37.66, 30.63) --
	( 40.67, 31.33) --
	( 43.67, 31.33) --
	( 46.68, 32.63) --
	( 49.68, 33.82) --
	( 52.69, 35.96) --
	( 55.70, 37.83) --
	( 58.70, 40.62) --
	( 61.71, 43.28) --
	( 64.71, 46.30) --
	( 67.72, 50.22) --
	( 70.73, 53.16) --
	( 73.73, 57.14) --
	( 76.74, 60.47) --
	( 79.74, 64.05) --
	( 82.75, 72.20) --
	( 85.75, 71.34) --
	( 88.76, 80.12) --
	( 91.77, 80.67) --
	( 94.77, 83.21) --
	( 97.78, 89.74) --
	(100.78, 87.61) --
	(103.79, 96.04) --
	(106.80, 98.47) --
	(109.80, 99.99) --
	(112.81,103.72) --
	(115.81,103.27) --
	(118.82,109.92) --
	(121.82,111.85) --
	(124.83,115.67) --
	(127.84,116.78) --
	(130.84,119.28) --
	(133.85,123.20) --
	(136.85,125.87);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 34.38) --
	( 37.66, 34.38) --
	( 40.67, 34.93) --
	( 43.67, 35.45) --
	( 46.68, 34.93) --
	( 49.68, 34.93) --
	( 52.69, 34.93) --
	( 55.70, 34.93) --
	( 58.70, 34.93) --
	( 61.71, 36.92) --
	( 64.71, 35.45) --
	( 67.72, 34.93) --
	( 70.73, 35.96) --
	( 73.73, 35.45) --
	( 76.74, 35.45) --
	( 79.74, 34.93) --
	( 82.75, 34.93) --
	( 85.75, 34.93) --
	( 88.76, 35.45) --
	( 91.77, 35.45) --
	( 94.77, 34.93) --
	( 97.78, 34.93) --
	(100.78, 35.45) --
	(103.79, 34.93) --
	(106.80, 36.92) --
	(109.80, 34.93) --
	(112.81, 35.45) --
	(115.81, 35.45) --
	(118.82, 34.93) --
	(121.82, 34.93) --
	(124.83, 34.93) --
	(127.84, 34.93) --
	(130.84, 34.93) --
	(133.85, 35.45) --
	(136.85, 34.93);
\definecolor{drawColor}{gray}{0.70}

@@

\path[fill=fillColor] (150.96,  8.58) rectangle (220.57, 58.93);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 32.28) {functions};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 17.82) {permutations};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.6 on 2024-04-23 11:24:49
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (240.29,135.16);
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{255,255,255}
\definecolor{fillColor}{RGB}{255,255,255}

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 54.53) --
	( 37.66, 54.50) --
	( 40.67, 54.50) --
	( 43.67, 54.49) --
	( 46.68, 54.49) --
	( 49.68, 54.49) --
	( 52.69, 54.49) --
	( 55.70, 54.50) --
	( 58.70, 54.50) --
	( 61.71, 54.49) --
	( 64.71, 54.49) --
	( 67.72, 54.49) --
	( 70.73, 54.49) --
	( 73.73, 54.49) --
	( 76.74, 54.50) --
	( 79.74, 54.50) --
	( 82.75, 54.50) --
	( 85.75, 54.50) --
	( 88.76, 54.49) --
	( 91.77, 54.50) --
	( 94.77, 54.50) --
	( 97.78, 54.49) --
	(100.78, 54.50) --
	(103.79, 54.50) --
	(106.80, 54.50) --
	(109.80, 54.50) --
	(112.81, 54.49) --
	(115.81, 54.50) --
	(118.82, 54.50) --
	(121.82, 54.50) --
	(124.83, 54.50) --
	(127.84, 54.50) --
	(130.84, 54.50) --
	(133.85, 54.50) --
	(136.85, 54.50);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 52.07) --
	( 37.66, 52.04) --
	( 40.67, 52.04) --
	( 43.67, 52.04) --
	( 46.68, 52.04) --
	( 49.68, 52.05) --
	( 52.69, 52.04) --
	( 55.70, 52.05) --
	( 58.70, 52.04) --
	( 61.71, 52.04) --
	( 64.71, 52.04) --
	( 67.72, 52.04) --
	( 70.73, 52.04) --
	( 73.73, 52.04) --
	( 76.74, 52.05) --
	( 79.74, 52.05) --
	( 82.75, 52.04) --
	( 85.75, 52.04) --
	( 88.76, 52.09) --
	( 91.77, 52.05) --
	( 94.77, 52.05) --
	( 97.78, 52.05) --
	(100.78, 52.05) --
	(103.79, 52.04) --
	(106.80, 52.04) --
	(109.80, 52.04) --
	(112.81, 52.04) --
	(115.81, 52.04) --
	(118.82, 52.04) --
	(121.82, 52.05) --
	(124.83, 52.05) --
	(127.84, 52.05) --
	(130.84, 52.04) --
	(133.85, 52.05) --
	(136.85, 52.04);
\definecolor{drawColor}{RGB}{217,95,2}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 49.39) --
	( 37.66, 49.33) --
	( 40.67, 49.33) --
	( 43.67, 49.33) --
	( 46.68, 49.33) --
	( 49.68, 49.33) --
	( 52.69, 49.33) --
	( 55.70, 49.35) --
	( 58.70, 49.35) --
	( 61.71, 49.33) --
	( 64.71, 49.33) --
	( 67.72, 49.33) --
	( 70.73, 49.33) --
	( 73.73, 49.33) --
	( 76.74, 49.33) --
	( 79.74, 49.35) --
	( 82.75, 49.35) --
	( 85.75, 49.35) --
	( 88.76, 49.33) --
	( 91.77, 49.33) --
	( 94.77, 49.33) --
	( 97.78, 49.33) --
	(100.78, 49.33) --
	(103.79, 49.33) --
	(106.80, 49.35) --
	(109.80, 49.35) --
	(112.81, 49.33) --
	(115.81, 49.33) --
	(118.82, 49.33) --
	(121.82, 49.33) --
	(124.83, 49.33) --
	(127.84, 49.33) --
	(130.84, 49.35) --
	(133.85, 49.35) --
	(136.85, 49.33);
\definecolor{drawColor}{RGB}{117,112,179}

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 34.66, 30.63) --
	( 37.66, 30.63) --
	( 40.67, 31.33) --
	( 43.67, 31.33) --
	( 46.68, 32.63) --
	( 49.68, 33.82) --
	( 52.69, 35.96) --
	( 55.70, 37.83) --
	( 58.70, 40.62) --
	( 61.71, 43.28) --
	( 64.71, 46.30) --
	( 67.72, 50.22) --
	( 70.73, 53.16) --
	( 73.73, 57.14) --
	( 76.74, 60.47) --
	( 79.74, 64.05) --
	( 82.75, 72.20) --
	( 85.75, 71.34) --
	( 88.76, 80.12) --
	( 91.77, 80.67) --
	( 94.77, 83.21) --
	( 97.78, 89.74) --
	(100.78, 87.61) --
	(103.79, 96.04) --
	(106.80, 98.47) --
	(109.80, 99.99) --
	(112.81,103.72) --
	(115.81,103.27) --
	(118.82,109.92) --
	(121.82,111.85) --
	(124.83,115.67) --
	(127.84,116.78) --
	(130.84,119.28) --
	(133.85,123.20) --
	(136.85,125.87);

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 29.90) --
	( 37.66, 30.63) --
	( 40.67, 30.63) --
	( 43.67, 29.90) --
	( 46.68, 30.63) --
	( 49.68, 31.33) --
	( 52.69, 32.63) --
	( 55.70, 33.82) --
	( 58.70, 35.45) --
	( 61.71, 38.26) --
	( 64.71, 40.62) --
	( 67.72, 42.34) --
	( 70.73, 46.05) --
	( 73.73, 49.23) --
	( 76.74, 52.36) --
	( 79.74, 64.35) --
	( 82.75, 58.30) --
	( 85.75, 68.19) --
	( 88.76, 70.67) --
	( 91.77, 72.59) --
	( 94.77, 78.45) --
	( 97.78, 78.57) --
	(100.78, 83.81) --
	(103.79, 86.56) --
	(106.80, 85.94) --
	(109.80, 92.57) --
	(112.81, 95.46) --
	(115.81, 98.41) --
	(118.82,102.64) --
	(121.82,102.38) --
	(124.83,106.28) --
	(127.84,110.72) --
	(130.84,112.06) --
	(133.85,116.16) --
	(136.85,119.03);
\definecolor{drawColor}{RGB}{231,41,138}

\path[draw=drawColor,line width= 0.6pt,dash pattern=on 2pt off 2pt ,line join=round] ( 34.66, 34.38) --
	( 37.66, 34.38) --
	( 40.67, 34.93) --
	( 43.67, 35.45) --
	( 46.68, 34.93) --
	( 49.68, 34.93) --
	( 52.69, 34.93) --
	( 55.70, 34.93) --
	( 58.70, 34.93) --
	( 61.71, 36.92) --
	( 64.71, 35.45) --
	( 67.72, 34.93) --
	( 70.73, 35.96) --
	( 73.73, 35.45) --
	( 76.74, 35.45) --
	( 79.74, 34.93) --
	( 82.75, 34.93) --
	( 85.75, 34.93) --
	( 88.76, 35.45) --
	( 91.77, 35.45) --
	( 94.77, 34.93) --
	( 97.78, 34.93) --
	(100.78, 35.45) --
	(103.79, 34.93) --
	(106.80, 36.92) --
	(109.80, 34.93) --
	(112.81, 35.45) --
	(115.81, 35.45) --
	(118.82, 34.93) --
	(121.82, 34.93) --
	(124.83, 34.93) --
	(127.84, 34.93) --
	(130.84, 34.93) --
	(133.85, 35.45) --
	(136.85, 34.93);
\definecolor{drawColor}{gray}{0.70}

@@

\path[fill=fillColor] (150.96,  8.58) rectangle (208.75, 58.93);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{fillColor}{RGB}{255,255,255}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 32.28) {bijections};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (240.29,135.16);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.72] at (174.42, 17.82) {functions};
\end{scope}
\end{tikzpicture}
